%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Ahmed Hussein Fekry}} & Email: \href{mailto:}{hussein.ahmed50@gmail.com}\\
  \href{https://fekry.dev}{Portfolio: fekry.dev} & Mobile:~~~+20-114-5566-153 \\
  \href{https://github.com/ahmedHusseinF}{Github: ~~github.com/ahmedHusseinF} \\
  \href{https://www.linkedin.com/in/ahmed-hussein-fekry/}{Linkedin: ~~ahmed-hussein-fekry} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cairo University}{Giza, Egypt}
      {Bachelor of Engineering - Computer Engineering;  GPA: 2.99}{July 2015 - June 2020}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Graduation Project:} Campus' Network Monitoring Solution / \textbf{Grade:} Excellent}}}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Javascript/Typescript, Java (11), C/C++, Golang, SQL, Bash/Zsh}
	\resumeSubItem{Frameworks}{~~~~Nodejs, Spring Boot, Deno, Angular 2+}
	\resumeSubItem{Platforms}{~~~~~~~Web, GCP, Linux, AWS}
	\resumeSubItem{Soft Skills}{~~~~~~~Time Management, Self Learning, Constructive feedback, Presentation Skills}

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{\href{https://eda.sw.siemens.com/en-US/}{Siemens EDA (former Mentor Graphics)}}{Cairo, Egypt}
    {Software Engineer (Full-time)}{Nov 2020 - Present}
    \resumeItemListStart
        \resumeItem{Refactoring}
          {Implemented some refactoring while providing new features for current products like \href{https://eda.sw.siemens.com/en-US/ic/questa/simulation/verification-management/}{Questa Verification Managment\textsuperscript{TM}} .}
          \resumeItem{Integration}
          {Responsible for OSLC integrations with multiple softwares like \href{https://polarion.plm.automation.siemens.com/}{Siemens Polarion\textsuperscript{TM}} or \href{https://www.ibm.com/docs/en/elm/6.0.6?topic=capabilities-rational-doors-next-generation}{IBM Rational DOORSNG\textsuperscript{TM}}.}
          \resumeItem{Legacy Software}{Responsible for maintaining \href{https://eda.sw.siemens.com/en-US/ic/questa/simulation/reqtracer/}{Questa ReqTracer\textsuperscript{TM}}  and providing support for product's customers new feature requests.}
      \resumeItemListEnd
%\vspace{-5pt}
    \resumeSubheading
		{\href{https://www.riseupsummit.com/home}{RiseUp co.}}{Cairo, Egypt}
		{Backend Engineer (Part-time, Contractual)}{July 2019 -  Nov 2020}
		\resumeItemListStart
        \resumeItem{Architecture}{Assisted in designing and implementing a microservice-based backend using Nest.js framework and gRPC.}
        \resumeItem{Product Engineering}{Designed and Created an in-house tool to manage large-scale workshop attendance system for a 4000 guest event.}
		\resumeItemListEnd
		
\resumeSubheading
		{\href{https://learnovia.com/en/}{Learnovia}}{Cairo, Egypt}
		{Frontend Engineer (Internship)}{May 2019 -  July 2019}
		\resumeItemListStart
        \resumeItem{Architecture}{Assisted in implementing a UI for eLearning Managment System using Angular 2+.}
        \resumeItem{Extensibility}{Created plugins to a Moodle learning managment system to extend its functionality and start integrating it into in-house tools.}
		\resumeItemListEnd

\resumeSubheading
	{\href{https://www.easykash.net/}{EasyKash (formerly PayMe Egypt)}}{Cairo, Egypt}
	{Backend Engineer (Internship)}{July 2017 -  Oct 2017}
	\resumeItemListStart
    \resumeItem{Planning}{Helped in planning and implementing features for a payment gateway developed in-house.}
    \resumeItem{Optimizations}{Engaged with senior developers to plan, implement and test query optimaztion for the payments flow using Node.js.}
	\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS (disabled for now)-----------------
\iffalse

\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Vison - multimedia search engine (NLP, Search Engine, Web Crawlers, Multimedia Processing)}{(Work in progress) Research oriented, open source, search engine for bringing reverse multimedia search to small \& mid scale enterprises. Tech: Python, NodeJS, Intel OpenVino Toolkit, Selenium, TensorFlow (October '18)}
\vspace{2pt}
\resumeSubItem{Reinforcement Learning based Traffic Control System (Reinforcement Learning, Computer Vision)}{AI model to resolve city traffic around 50\%
faster. Tech: Python, Alibaba Cloud, Raspberry Pi, Arduino, SUMO \& OpenCV. (August '18)}
\vspace{2pt}
\resumeSubItem{Panorama from Satellite Imagery using Distributed Computing (Distributed Computing, Image Processing)}{Images clicked using drones, provided by ISRO were stitched together using distributed public compute nodes, effectively bringing down processing time exponentially. Tech: PHP, C++, Java, Python (March '18)}
\vspace{2pt}
\resumeSubItem{Drag-n-drop machine learning learning environment (Web Development, Machine Learning)}{Scratch like tool for implementing machine learning pipelines along with built in tutorial for each concept. Tech: Python, JavaScript (September '18)}
\vspace{2pt}
\resumeSubItem{Search Engine and Social Network(Web Development, Web Crawler, Search)}{Created from scratch a social network and a search engine based on the idea of integrating Facebook and Google. The launched website was among top 1000 websites in India during 2012-2013. Tech: PHP, MySQL, HTML, CSS, WebSockets, JavaScript, RSS, XML ( May '12)}
\resumeSubHeadingListEnd

\fi



\vspace{-5pt}
\section{Volunteer Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
    {Software Engineer at Cairo University Racing Team}{Cairo, Egypt}
    {Helped in integrating a digital dashboard with a Raspberry Pi for data collection.}{Jan 2019 - Jan 2020}
\vspace{5pt}
    \resumeSubheading
    {Workshops Coordinator at TEDxCairoUniversity}{Cairo, Egypt}
    {Conducted workshops internally about tech empowerment.}{Jan 2017 - Dec 2017}

\resumeSubHeadingListEnd

\end{document}